---
title: "Association Rules"
output: pdf_document
---

Composed by: Akihiro Hayashi

#Introduction

Processes:

1. Support(X -> Y) = P(X, Y) >= minsup
2. Confidence(X -> Y) = P(Y|X) = P(X, Y) / P(X) >= mincon
3. Lift(X -> Y) = P(Y|X) / P(Y) = Confidence(X -> Y) / P(Y)

Applications:

1. Promotion (target = "rules")
2. Sales Ranking (target = "frequent itemsets")
2. Bundle (target = "frequent itemsets")

#Tools

arules or eclat

```{r}
install.packages("arules")
library(arules)
```

##Methods

1. apriori(data, parameter = NULL, appearance = NULL, control = NULL)

parameter: support / confidence / maxlen / minlen / target = "rules" or "frequent itemsets"
appearance: lhs / rhs
control: 1 / -1

2. eclat(data, parameter = NULL, control = NULL)

target: cannot be "rules"
maxlen: default = 5

#Association Rules

##Step 0. Data

```{r}
data("Groceries")
summary(Groceries)
inspect(Groceries[1:10])
```

##Step 1. Associate

```{r}
rules0 <- apriori(Groceries, parameter = list(support = .001, confidence = .5))

rules0
inspect(rules0[1:10])
```

We got too many rules.

###Increase Support & Confidence

```{r}
rules1 <- apriori(Groceries, parameter = list(support = .005, confidence = .5))
rules1

rules2 <- apriori(Groceries, parameter = list(support = .005, confidence = .6))
rules2

rules3 <- apriori(Groceries, parameter = list(support = .005, confidence = .64))
rules3

inspect(rules3)
```

###Increase Support

```{r}
rules.sorted_sup <- sort(rules0, by = "support")
inspect(rules.sorted_sup[1:5])
```

###Increase Confidence

```{r}
rules.sorted_con <- sort(rules0, by = "confidence")
inspect(rules.sorted_con[1:5])
```

###Increase Lift

```{r}
rules.sorted_lift <- sort(rules0, by = "lift")
inspect(rules.sorted_lift[1:5])
```

#Application

##Promote ("mustard")

```{r}
rules4 <- apriori(Groceries, parameter = list(maxlen = 2, supp = .001, conf = .1), appearance = list(rhs = "mustard", default = "lhs"))
inspect(rules4)
```


If our target is "frequent itemsets", we only need to set "supp". Check following applications.

##Sales Ranking

```{r}
itemsets_apr <- apriori(Groceries, parameter = list(supp = .001, target = "frequent itemsets"), control = list(sort = -1))
itemsets_apr
inspect(itemsets_apr[1:5])
```

##Bundle

```{r}
itemsets_ecl <- eclat(Groceries, parameter = list(minlen = 1, maxlen = 3, supp = .001, target = "frequent itemsets"), control = list(sort = -1))
itemsets_ecl
inspect(itemsets_ecl[1:5])
```

#Visualization

```{r}
install.packages("arulesViz")
library(arulesViz)
```

```{r}
rules5 <- apriori(Groceries, parameter = list(supp = .002, conf = .5))
rules5
plot(rules5)
plot(rules5, interactive = TRUE)
```

```{r}
plot(rules5, interactive = TRUE)
```

```{r}
plot(rules5, shading = "order", control = list(main = "Two key plot"))
```

```{r}
plot(rules5, method = "grouped")
```

```{r}
plot(rules5, method = "matrix")
```

```{r}
plot(rules5, method = "matrix3D")
```

```{r}
plot(rules5, method = "paracoord")
```

#Summary

Package: arules, arules

Dataset: Groceries

Functions: apriori(), eclat(), inspect(), sort(), plot()